This is the cleaning file for e1-4 for data in the public repo. all csv's written out of here go in ted_paper_analyses.rmd


### Set global seed and output location
```{r}
# set a seed
set.seed(42)

require(knitr)         # for knitting
library(readxl)        # for reading Excel files
library(lme4)          # for mixed effects models 
library(Hmisc)         # for bootstrapped confidence intervals
library(ggeffects)     # for logistic regression outputs
library(showtext)      # for fonts
library(broom.mixed)   # for augmenting fitted models
library(png)           # for working with images
library(grid)
library(patchwork)     # for multiple plots
library(tidyverse)     # for everything else
library(viridis)
library(here)
library(emmeans)
library(langcog)
library(boot)
library(pbkrtest)
library(kableExtra)

# set the export directory using here()
export_dir <- here("data", "clean")
inport_dir <- here("data", "raw")
```


## Experiment 1 (US Adults Graded Judgments)

Read in data:

```{r}
#load in build data
df.e1_buildtask_raw <- read.csv(here(inport_dir, "e1_buildtask.csv"))

#load in time data
df.e1_time_raw <- read.csv(here(inport_dir, "e1_time_estimation.csv"))

#load in difficulty data
df.e1_difficulty_raw <- read.csv(here(inport_dir, "e1_diff_estimation.csv"))
```

Processing Build Task:

```{r}

# First, create a mapping of trial values to their respective labels
build_trial_labels <- c("7_Number", 
                        "8_Number", 
                        "9_InitNumber", 
                        "10_Stability", 
                        "11_InitSorted", 
                        "12_Number", 
                        "13_Sampling", 
                        "14_Stability", 
                        "15_Number", 
                        "16_Number", 
                        "17_InitNumber", 
                        "18_Stability", 
                        "19_Pattern", 
                        "20_Stability", 
                        "21_Number", 
                        "22_Number", 
                        "23_InitNumber", 
                        "24_Stability", 
                        "25_InitSorted", 
                        "26_Number", 
                        "27_Sampling", 
                        "28_Stability", 
                        "29_Number", 
                        "30_Number",
                        "31_InitNumber",
                        "32_Stability",
                        "33_Pattern",
                        "34_Stability",
                        "35_Distance",
                        "36_Distance")

##Exclude participants
df.e1_buildtask = subset(df.e1_buildtask_raw, df.e1_buildtask_raw$id != "BuildTask_170421_01")
df.e1_buildtask = subset(df.e1_buildtask, df.e1_buildtask$id != "BuildTask_170426_02") #no data
df.e1_buildtask = subset(df.e1_buildtask, df.e1_buildtask$id != "BuildTask_170526_01") #no data

#factors
df.e1_buildtask$id = factor(df.e1_buildtask$id)
df.e1_buildtask$trial = factor(df.e1_buildtask$trial)

df.e1_buildtask <- df.e1_buildtask |> 
  na.omit() %>%
  gather(easy_hard, build_time,c("easy", "hard")) %>%
  select(id, trial, easy_hard, build_time) %>%
  na.omit() %>%
  group_by(trial,easy_hard) %>%
  filter(id != "BuildTask_170630",
         id != "BuildTask_170526_03") |> 
  ungroup()

# Ensure the trials are sorted in increasing order
build_sorted_trials <- sort(unique(df.e1_buildtask$trial))

# Create a named vector to map sorted trials to labels
names(build_trial_labels) <- build_sorted_trials

# Assign the 'trial' column using the mapping
df.e1_buildtask$trial <- factor(df.e1_buildtask$trial, labels = build_trial_labels[as.character(build_sorted_trials)])


df.e1_buildtask_summary <- df.e1_buildtask |> 
  # get rid of trials that were not administered in the Time or Difficulty estimation
  filter(!grepl("35_Distance", trial)) |> 
  filter(!grepl("36_Distance", trial)) |>
  filter(!grepl("32_Stability", trial)) |>
  # get rid of trials that cannot be modeled
  filter(trial != "10_Stability") |> 
  filter(trial != "24_Stability") |> 
  select(id, trial, build_time, easy_hard) |> 
  group_by(trial, easy_hard) |> 
  na.omit() |> 
  summarize(mean_build = mean(build_time))
```

Processing Time Estimation:

```{r}
# First, create a mapping of trial values to their respective labels
time_trial_labels <- c("7_Number", 
                       "8_Number", 
                       "9_InitNumber", 
                       "10_Stability", 
                       "11_InitSorted", 
                       "12_Number", 
                       "13_Sampling", 
                       "14_Stability", 
                       "15_Number", 
                       "16_Number", 
                       "17_InitNumber", 
                       "18_Stability", 
                       "19_Pattern", 
                       "20_Stability", 
                       "21_Number",
                       "22_Number", 
                       "23_InitNumber", 
                       "24_Stability", 
                       "25_InitSorted", 
                       "26_Number",
                       "27_Sampling", 
                       "28_Stability", 
                       "29_Number", 
                       "30_Number", 
                       "31_InitNumber",
                       "33_Pattern", 
                       "34_Stability", 
                       "37_Practice")

#initial cleaning
df.e1_time <- df.e1_time_raw |> 
  separate(trial, into = c("trial","easy_hard")) %>%
  select(id,age,gender,trial,easy_hard,rating) |> 
  mutate(easy_hard = factor(easy_hard, levels=c(1,2), labels=c("easy","hard"))) 

df.e1_time$trial <- as.numeric(df.e1_time$trial)

# Ensure the trials are sorted in increasing order
time_sorted_trials <- sort(unique(df.e1_time$trial))

# Create a named vector to map sorted trials to labels
names(time_trial_labels) <- time_sorted_trials

# Assign the 'trial' column using the mapping
df.e1_time$trial <- factor(df.e1_time$trial, labels = time_trial_labels[as.character(time_sorted_trials)])

df.e1_time_clean <- df.e1_time |> 
  group_by(id) %>%
  #filtering our participants who gave the same response on all trials
  filter(sd(rating) != 0) |> 
  ungroup() |> 
  #get rid of warm-up trial
  filter(trial != "37_Practice") |> 
  # take out trials that are not modelable
  filter(trial != "10_Stability") |> 
  filter(trial != "24_Stability")


df.e1_time_summary <- df.e1_time_clean |> 
  select(id,trial,rating,easy_hard) %>%
  #mutate(trial = all_trial) %>%
  #select(id,trial,condition,rating) %>%
  group_by(trial,easy_hard) %>%
  summarise(mean_time= (mean(rating)))

```

Process Difficulty Data:

```{r}

# First, create a mapping of trial values to their respective labels
diff_trial_labels <- c("7_Number", 
                        "8_Number", 
                        "9_InitNumber", 
                        "10_Stability", 
                        "11_InitSorted", 
                        "12_Number", 
                        "13_Sampling", 
                        "14_Stability", 
                        "15_Number", 
                        "16_Number", 
                        "17_InitNumber", 
                        "18_Stability", 
                        "19_Pattern", 
                        "20_Stability", 
                        "21_Number", 
                        "22_Number", 
                        "23_InitNumber", 
                        "24_Stability", 
                        "25_InitSorted", 
                        "26_Number", 
                        "27_Sampling", 
                        "28_Stability", 
                        "29_Number", 
                        "30_Number",
                        "31_InitNumber",
                        "33_Pattern",
                        "34_Stability",
                        "35_Distance",
                        "36_Distance")

#initial cleaning
df.e1_difficulty <- df.e1_difficulty_raw |> 
  separate(trial, into = c("trial","easy_hard")) %>%
  select(id,age,gender,trial,easy_hard,rating) |>
  mutate(easy_hard = factor(easy_hard, levels=c(1,2), labels=c("easy","hard")))|>
  group_by(id, trial) |> 
  #trial 31 administered twice, take only the first observation
  mutate(trial_count = row_number(trial == 31)) |> 
  filter(!(trial == 31 & trial_count > 2)) |> 
  select(!trial_count) |> 
  ungroup()

# Convert the 'trial' column to numeric if it is not already
df.e1_difficulty$trial <- as.numeric(df.e1_difficulty$trial)

# Ensure the trials are sorted in increasing order
diff_sorted_trials <- sort(unique(df.e1_difficulty$trial))

# Create a named vector to map sorted trials to labels
names(diff_trial_labels) <- diff_sorted_trials

# Assign the 'trial' column using the mapping
df.e1_difficulty$trial <- factor(df.e1_difficulty$trial, labels = diff_trial_labels[as.character(diff_sorted_trials)])

df.e1_difficulty_clean <- df.e1_difficulty |>
  group_by(id) %>%
  #get rid of participants who gave teh same answer
  filter(sd(rating) != 0) |>
  ungroup()

df.e1_difficulty_summary <- df.e1_difficulty_clean |> 
  filter(!grepl("35_Distance", trial)) |> 
  filter(!grepl("36_Distance", trial)) |>
  select(id,trial,rating,easy_hard) %>%
  group_by(trial,easy_hard) %>%
  summarise(mean_diff= (mean(rating))) |> 
  # take out trials that are not modelable
  filter(trial != "10_Stability") |> 
  filter(trial != "24_Stability")

df.e1_difficulty_exclude <- df.e1_difficulty |>
  group_by(id) %>%
  #get rid of participants who gave the same answer
  filter(sd(rating) == 0) |>
  ungroup()

df.e1_difficulty_exclude |> 
  group_by(id) |> 
  summarize(n = n())

```

Now let's anonymize & export

```{r}
# Remove "BuildTask_" prefix from build task IDs
df.e1_buildtask <- df.e1_buildtask %>%
  mutate(id = gsub("BuildTask_", "", id))  # Remove the "BuildTask_" prefix

# Create a unique list of IDs from all dataframes
unique_ids_e1 <- unique(c(df.e1_buildtask$id, df.e1_time$id, df.e1_difficulty$id))

# Generate 8-digit random numbers
new_ids_e1 <- sample(10000000:99999999, length(unique_ids_e1), replace = FALSE)

# Create mapping
id_mapping <- setNames(new_ids_e1, unique_ids_e1)

# Anonymize IDs in the build task dataframe
df.e1_buildtask <- df.e1_buildtask %>%
  mutate(id = id_mapping[as.character(id)])

# Anonymize IDs in the time dataframe
df.e1_time <- df.e1_time %>%
  mutate(id = id_mapping[as.character(id)])

# Anonymize IDs in the difficulty dataframe
df.e1_difficulty <- df.e1_difficulty %>%
  mutate(id = id_mapping[as.character(id)])

# Export the dataframes
write.csv(df.e1_buildtask, file = here(export_dir, "e1_buildtask.csv"), row.names = FALSE)
write.csv(df.e1_time, file = here(export_dir, "e1_time.csv"), row.names = FALSE)
write.csv(df.e1_difficulty, file = here(export_dir, "e1_difficulty.csv"), row.names = FALSE)
```




# Experiment 2a

```{r}
# Load data in
df.e2adultfc_e <- read.csv(here(inport_dir, "e2a_adultfc_easy.csv"))

df.e2adultfc_easy = as.data.frame(df.e2adultfc_e[which(df.e2adultfc_e$include == '1'),])

df.e2adultfc_easy_drop = as.data.frame(df.e2adultfc_e[which(df.e2adultfc_e$include == '0'),])

df.e2adultfc_h <- read.csv(here(inport_dir, "e2a_adultfc_hard.csv"))

df.e2adultfc_hard = as.data.frame(df.e2adultfc_h[which(df.e2adultfc_h$include == '1'),])

df.e2adultfc_hard_drop = as.data.frame(df.e2adultfc_h[which(df.e2adultfc_h$include == '0'),])


# Selecting columns of interest
df.e2adultfc_easy <- select(df.e2adultfc_easy, 
                            id, 
                            group, 
                            condition, 
                            InsR, 
                            Sampling_Check1, 
                            Sampling_Check2, 
                            Age_Check1, 
                            Age_Check2, 
                            Sling_Check1, 
                            Sling_Check2, 
                            Number_TriCir, 
                            Number_Cross, 
                            Number_Vert, 
                            Number_Horz, 
                            Init_Horz, 
                            Init_Vert, 
                            TwoBlocks_TenBlocks, 
                            Init_Distance, 
                            Fin_Distance, 
                            Init_Sorted, 
                            Pattern_NoPattern, 
                            Sampling, 
                            Box_Castle, 
                            TwoPile_Castle, 
                            Vert_Horz, 
                            Adult_Child, 
                            Sling_TwoHands, 
                            OneAgent_TwoAgent, 
                            age, 
                            gender,
                            include, 
                            include_why)

df.e2adultfc_easy_drop <- select(df.e2adultfc_easy_drop, 
                                 id, 
                                 group, 
                                 condition, 
                                 InsR, 
                                 Sampling_Check1, 
                                 Sampling_Check2, 
                                 Age_Check1, 
                                 Age_Check2, 
                                 Sling_Check1, 
                                 Sling_Check2, 
                                 Number_TriCir, 
                                 Number_Cross, 
                                 Number_Vert, 
                                 Number_Horz, 
                                 Init_Horz, 
                                 Init_Vert, 
                                 TwoBlocks_TenBlocks, 
                                 Init_Distance, 
                                 Fin_Distance, 
                                 Init_Sorted, 
                                 Pattern_NoPattern, 
                                 Sampling, 
                                 Box_Castle,
                                 TwoPile_Castle, 
                                 Vert_Horz, 
                                 Adult_Child, 
                                 Sling_TwoHands, 
                                 OneAgent_TwoAgent, 
                                 age, 
                                 gender, 
                                 include, 
                                 include_why)

df.e2adultfc_hard <- select(df.e2adultfc_hard, 
                            id, 
                            group, 
                            condition, 
                            InsR, 
                            Sampling_Check1, 
                            Sampling_Check2, 
                            Age_Check1, 
                            Age_Check2, 
                            Sling_Check1, 
                            Sling_Check2, 
                            Number_TriCir, 
                            Number_Cross, 
                            Number_Vert, 
                            Number_Horz, 
                            Init_Horz, 
                            Init_Vert, 
                            TwoBlocks_TenBlocks, 
                            Init_Distance, 
                            Fin_Distance, 
                            Init_Sorted, 
                            Pattern_NoPattern, 
                            Sampling, 
                            Box_Castle,
                            TwoPile_Castle, 
                            Vert_Horz, 
                            Adult_Child, 
                            Sling_TwoHands, 
                            OneAgent_TwoAgent, 
                            age, 
                            gender, 
                            include, 
                            include_why)

df.e2adultfc_hard_drop <- select(df.e2adultfc_hard_drop, 
                                 id, 
                                 group, 
                                 condition, 
                                 InsR, 
                                 Sampling_Check1, 
                                 Sampling_Check2, 
                                 Age_Check1, 
                                 Age_Check2, 
                                 Sling_Check1, 
                                 Sling_Check2, 
                                 Number_TriCir, 
                                 Number_Cross, 
                                 Number_Vert, 
                                 Number_Horz, 
                                 Init_Horz, 
                                 Init_Vert, 
                                 TwoBlocks_TenBlocks, 
                                 Init_Distance, 
                                 Fin_Distance, 
                                 Init_Sorted, 
                                 Pattern_NoPattern, 
                                 Sampling, 
                                 Box_Castle,
                                 TwoPile_Castle, 
                                 Vert_Horz, 
                                 Adult_Child, 
                                 Sling_TwoHands, 
                                 OneAgent_TwoAgent, 
                                 age, 
                                 gender, 
                                 include, 
                                 include_why)


# Merging Data Frames
df.e2adultfc_all <- full_join(df.e2adultfc_easy, df.e2adultfc_hard)

df.e2adultfc_all_drop <- full_join(df.e2adultfc_easy_drop, df.e2adultfc_hard_drop)

# Selecting columns of interest in merged Data Frame
df.e2adultfc_all <- select(df.e2adultfc_all, 
                           id, 
                           condition, 
                           age, 
                           gender, 
                           Number_TriCir, 
                           Number_Cross, 
                           Number_Vert, 
                           Number_Horz, 
                           Init_Horz, 
                           Init_Vert, 
                           TwoBlocks_TenBlocks,
                           Pattern_NoPattern, 
                           Sampling, 
                           TwoPile_Castle, 
                           Vert_Horz, 
                           Adult_Child, 
                           Sling_TwoHands, 
                           OneAgent_TwoAgent) 

df.e2adultfc_all_drop <- select(df.e2adultfc_all_drop, 
                                id, 
                                condition, 
                                age, 
                                gender, 
                                Number_TriCir, 
                                Number_Cross, 
                                Number_Vert, 
                                Number_Horz, 
                                Init_Horz, 
                                Init_Vert, 
                                TwoBlocks_TenBlocks,
                                Pattern_NoPattern, 
                                Sampling, 
                                TwoPile_Castle, 
                                Vert_Horz, 
                                Adult_Child, 
                                Sling_TwoHands, 
                                OneAgent_TwoAgent) 

# Reshape to long format and assign trial types
df.e2adultfc_all_long <- df.e2adultfc_all %>%
  gather(trial,correct,
        Number_TriCir,
        Number_Cross,
        Number_Vert,
        Number_Horz,
        Init_Horz,
        Init_Vert,
        TwoBlocks_TenBlocks,
        Pattern_NoPattern,
        Sampling,
        TwoPile_Castle,
        Vert_Horz,
        Adult_Child,
        Sling_TwoHands,
        OneAgent_TwoAgent) %>%
  rename(question_type = condition) %>%
  mutate(condition = ifelse(trial == "Number_TriCir"| trial == "Number_Cross"| trial == "Number_Vert" |trial == "Number_Horz" | trial == "TwoBlocks_TenBlocks" | trial == "TwoPile_Castle" | trial == "Vert_Horz", "Simple", ifelse(trial == "Sampling" | trial == "Pattern_NoPattern"| trial == "Init_Horz" | trial == "Init_Vert", "Complex", "Agent"))) %>%
  na.omit()

#Adults: all data drop
df.e2adultfc_all_drop_long <- df.e2adultfc_all_drop %>%
  gather(trial,correct,
        Number_TriCir,
        Number_Cross,
        Number_Vert,
        Number_Horz,
        Init_Horz,
        Init_Vert,
        TwoBlocks_TenBlocks,
        Pattern_NoPattern,
        Sampling,
        TwoPile_Castle,
        Vert_Horz,
        Adult_Child,
        Sling_TwoHands,
        OneAgent_TwoAgent) %>%
  rename(question_type = condition) %>%
  mutate(condition = ifelse(trial == "Number_TriCir"| trial == "Number_Cross" | trial == "Number_Vert" | trial == "Number_Horz" |trial == "TwoBlocks_TenBlocks" | trial == "TwoPile_Castle" | trial == "Vert_Horz", "Simple", ifelse(trial == "Sampling" | trial == "Pattern_NoPattern"| trial == "Init_Horz" | trial == "Init_Vert", "Complex", "Agent"))) %>%
  na.omit()
```



Change trial names, summarize:

```{r}
# Changing trial names to new format
df.e2adultfc_all_long <- df.e2adultfc_all_long |> 
    mutate(trial = case_when(trial == "Number_TriCir" ~ "Number1",
                           trial == "Number_Cross" ~ "Number2",
                           trial == "Number_Vert" ~ "Number3",
                           trial == "Number_Horz" ~ "Number4",
                           trial == "Vert_Horz" ~ "Stability",
                           trial == "TwoBlocks_TenBlocks" ~ "Number&Stability",
                           trial == "Init_Horz" ~ "Process1",
                           trial == "Init_Vert" ~ "Process2",
                           trial == "Pattern_NoPattern" ~ "Pattern",
                           trial == "Sampling" ~ "Probability",
                           trial == "Sling_TwoHands" ~ "Agent1",
                           trial == "Adult_Child" ~ "Agent2",
                           trial == "OneAgent_TwoAgent" ~ "Agent3",
                           .default = trial))

# Summarize exp 2 adult results in new data frame
df.e2adultfc_summary <- df.e2adultfc_all_long |> 
  mutate(dataset = "US Adults") |>
  group_by(trial) |> 
  multi_boot_standard(col = "correct") |> 
  mutate(dataset = "US Adults")

```


Now let's anonymize & export for e2a
```{r}
# Create a unique list of IDs from all dataframes
unique_ids_e2a <- unique(c(df.e2adultfc_all$id))

# Generate 8-digit random numbers
new_ids_e2a <- sample(10000000:99999999, length(unique_ids_e2a), replace = FALSE)

# Create mapping
id_mapping <- setNames(new_ids_e2a, unique_ids_e2a)

# Anonymize IDs in the build task dataframe
df.e2adultfc_all <- df.e2adultfc_all %>%
  mutate(id = id_mapping[as.character(id)])

# Export the dataframes
write.csv(df.e2adultfc_all, file = here(export_dir, "e2adultfc_all.csv"), row.names = FALSE)
```


## Experiment 2b (US Child Forced Choice)

```{r}
# Read in data
df.e2b_childfc_raw <- read.csv(here(inport_dir, "e2b_childfc.csv"), header = T)

#Change Trial Names
df.e2b_childfc <- df.e2b_childfc_raw |> 
    mutate(trial = case_when(trial_name == "Number_TriCir" ~ "Number1",
                           trial_name == "Number_Cross" ~ "Number2",
                           trial_name == "Number_Vert" ~ "Number3",
                           trial_name == "Number_Horz" ~ "Number4",
                           trial_name == "Stability1" ~ "Stability",
                           trial_name == "Num_Stab" ~ "Number&Stability",
                           trial_name == "Init_Horz" ~ "Process1",
                           trial_name == "Init_Vert" ~ "Process2",
                           trial_name == "Process3" ~ "Pattern",
                           trial_name == "Sampling" ~ "Probability",
                           trial_name == "Sling" ~ "Agent1",
                           trial_name == "Child_Adult" ~ "Agent2",
                           trial_name == "Cooperation" ~ "Agent3",
                           .default = trial_name)) |> 
  select(-trial_name)

#ensure trial naming is right
df.e2b_childfc |> 
  group_by(trial) |> 
  summarize(n = n())

#get rid of NAs
df.e2b_childfc <- df.e2b_childfc |> 
  filter(!is.na(trial))

```

Now let's anonymize & export for e2b
```{r}
# Create a unique list of IDs from all dataframes
unique_ids_e2b <- unique(df.e2b_childfc$subject)

# Generate 8-digit random numbers
new_ids_e2b <- sample(10000000:99999999, length(unique_ids_e2b), replace = FALSE)

# Create mapping
id_mapping <- setNames(as.character(new_ids_e2b), as.character(unique_ids_e2b))

# Anonymize IDs, rename the column, and drop the "X" column
df.e2b_childfc <- df.e2b_childfc %>%
  mutate(id = as.numeric(id_mapping[as.character(subject)])) %>%
  select(-subject, -X) %>%
  select(id, everything())

# Export the dataframes
write.csv(df.e2b_childfc, file = here(export_dir, "e2b_childfc.csv"), row.names = FALSE)
```



## Experiment 3 (Tsimane' Children)

```{r}

#Read in data
df.e3childfc_raw <- read_excel(here(inport_dir, "e3_childfc.xlsx"), sheet = 2)

```

Clean and Change Trial Names:

```{r}

# Clean data
df.e3childfc = df.e3childfc_raw %>%
  transmute(trial = Trial,
            order = PresentationOrder,
            faster = Faster,
            counterbalancing = Counterbalancing,
            gender = Gender,
            age = as.numeric(Age),
            school = Schoolig,
            condition = Category,
            id = Id,
            correct = Harder_acc) %>%
  mutate(trial = factor(trial, levels=c("1","2","3","4","5","6","7","11","12","15"), labels=c("Number_TriCir","Number_Cross","Number_Vert","Number_Horz","Init_Horz","Init_Vert","TwoBlock_TenBlock","Pattern","Sampling","Vert_Horz"))) %>%
  mutate(condition = ifelse(trial== "Number_TriCir" | trial == "Number_Cross" | trial == "Number_Vert" | trial == "Number_Horz" | trial == "TwoBlock_TenBlock" | trial == "Vert_Horz", "Simple", "Complex")) %>%
    na.omit() %>% # there are two kids with no bday info
  mutate(ageBin = ifelse(age < median(age),"5-8","9-13"))


#renaming trials
df.e3childfc <- df.e3childfc |> 
  mutate(trial = case_when(trial == "Number_TriCir" ~ "Number1",
                           trial == "Number_Cross" ~ "Number2",
                           trial == "Number_Vert" ~ "Number3",
                           trial == "Number_Horz" ~ "Number4",
                           trial == "Vert_Horz" ~ "Stability",
                           trial == "TwoBlock_TenBlock" ~ "Number&Stability",
                           trial == "Init_Horz" ~ "Process1",
                           trial == "Init_Vert" ~ "Process2",
                           trial == "Pattern" ~ "Pattern",
                           trial == "Sampling" ~ "Probability",
                           .default = trial))

```

Now let's anonymize & export for e3
```{r}
# Create a unique list of IDs from all dataframes
unique_ids_e3 <- unique(df.e3childfc$id)

# Generate 8-digit random numbers
new_ids_e3 <- sample(10000000:99999999, length(unique_ids_e3), replace = FALSE)

# Create mapping
id_mapping <- setNames(as.character(new_ids_e3), as.character(unique_ids_e3))

# Anonymize IDs in the build task dataframe
df.e3childfc <- df.e3childfc %>%
  mutate(id = id_mapping[as.character(id)])

# Export the dataframes
write.csv(df.e3childfc, file = here(export_dir, "e3childfc.csv"), row.names = FALSE)
```


## Experiment 4 (VR)

Read in data:

```{r}

df.e4_vr_raw <- read.csv(here(inport_dir, "e4_vrdata.csv"), header = T)

```

Clean data:

```{r}
#Exclusions
df.e4_vr <- df.e4_vr_raw |> 
  filter(id != "") |> 
  filter(Exclude. == 0) |> 
  select(id, Friction_Level, contains("Difficulty"), contains("Sec"),
         Gender, Age)

# Renaming Trial Conditions for both difficulty and time
e4_tower_names <- c(X5H_Difficulty = "5 Horizontal", 
               X10H_Difficulty = "10 Horizontal", 
               X3x3_Difficulty = "3x3", 
               X5V_Difficulty = "5 Vertical", 
               LShape_Difficulty = "L-Shaped", 
               X10V_Difficulty = "10 Vertical")

# Reshape difficulty data
df.e4_vr_diff <- df.e4_vr %>% 
  select(id, Friction_Level, contains("Difficulty"), Gender, Age) %>%
  gather(key = "Tower_Type", 
         value = "Difficulty",
         X5H_Difficulty:LShape_Difficulty, 
         factor_key = TRUE)

# Reshape time data
df.e4_vr_time <- df.e4_vr %>% 
  select(id, Friction_Level, contains("Sec"), Gender, Age) %>%
  gather(key = "Tower_Type", 
         value = "Time",
         X5H_Sec:LShape_Sec, 
         factor_key = TRUE)

# Clean up the Tower_Type names to match
df.e4_vr_time$Tower_Type <- gsub("_Sec", "_Difficulty", df.e4_vr_time$Tower_Type)

# Combine the dataframes
df.e4_vr <- df.e4_vr_diff %>%
  left_join(df.e4_vr_time, by = c("id", "Friction_Level", "Gender", "Age", "Tower_Type"))

# Rest of processing
df.e4_vr$Difficulty <- as.numeric(as.character(df.e4_vr$Difficulty))
df.e4_vr$Time <- as.numeric(as.character(df.e4_vr$Time))
df.e4_vr$Tower_Type <- factor(df.e4_vr$Tower_Type, 
                              levels = names(e4_tower_names), 
                              labels = e4_tower_names)

# Convert columns to factor
df.e4_vr <- df.e4_vr |> 
  mutate(Friction_Level = as.factor(Friction_Level))


```


Now let's anonymize & export for e4
```{r}
# Anonymization and export
unique_ids_e4 <- unique(df.e4_vr$id)
new_ids_e4 <- sample(10000000:99999999, length(unique_ids_e4), replace = FALSE)
id_mapping <- setNames(as.character(new_ids_e4), as.character(unique_ids_e4))
df.e4_vr <- df.e4_vr %>%
  mutate(id = id_mapping[as.character(id)])
write.csv(df.e4_vr, file = here(export_dir, "e4childfc.csv"), row.names = FALSE)
```


## SOM: In-Person Developmental

```{r}

# Reading in data
df.som_inpersondev_raw <- read.csv(here(inport_dir, "som_inperson_dev.csv"), header = T)

```


rename trials:

```{r}

df.som_inpersondev <- df.som_inpersondev_raw |> 
    mutate(trial = case_when(trial == "Number_TriCir" ~ "Number1",
                           trial == "Number_Cross" ~ "Number2",
                           trial == "Number_Vert" ~ "Number3",
                           trial == "Number_Horz" ~ "Number4",
                           trial == "Vert_Horz" ~ "Stability",
                           trial == "TwoBlock_TenBlock" ~ "Number&Stability",
                           trial == "Init_Horz" ~ "Process1",
                           trial == "Init_Vert" ~ "Process2",
                           trial == "Pattern_NoPattern" ~ "Pattern",
                           trial == "Sampling" ~ "Probability",
                           trial == "Sling_TwoHands" ~ "Agent1",
                           trial == "Adult_Child" ~ "Agent2",
                           trial == "OneAgent_TwoAgent" ~ "Agent3",
                           .default = trial)) |> 
  mutate(gender = ifelse(gender == 1, "Female", "Male"))

```


Now let's anonymize & export for SOM
```{r}
# Create a unique list of IDs from all dataframes
unique_ids_som <- unique(df.som_inpersondev$id)

# Generate 8-digit random numbers
new_ids_som <- sample(10000000:99999999, length(unique_ids_som), replace = FALSE)

# Create mapping
id_mapping <- setNames(as.character(new_ids_som), as.character(unique_ids_som))

# Anonymize IDs in the build task dataframe
df.som_inpersondev <- df.som_inpersondev %>%
  mutate(id = id_mapping[as.character(id)]) %>%
  select(-X)

# Export the dataframes
write.csv(df.som_inpersondev, file = here(export_dir, "som_inpersondev.csv"), row.names = FALSE)
```
